2019 Draft Prep

### 2019-03-23 draftPrep.Rmd
Minor knitr adjustments

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(stop_on_error = 2L)
source("R/yahoo_api.R")
source("R/z_scores.R")
options(tidyverse.quiet=TRUE)
library(knitr)
library(plotly)
library(tidyverse)
```

@@

Some observations from this plot:
- Batters are in general weighed higher than pitchers since there are more categories with which to add to the z_sum
- Andrew Miller-like relievers are valued higher than ADP due to their high inning total and low ratio stats (ERA, WHIP)
- Ace starting pitchers and traditional closers are valued less than ADP despite their relative scarcity. 
  - Aces are the players most affected by not adjusting the z_score weighting for pitchers
  - Even with adjustment, tradtional closers have a lesser inning count nor have significant input in other categories to adjust their z_score very much

@@

```{r include=FALSE}

@@

# Draft Prep
Armed with this information, here's what I need before the draft:
1. Exclude known keepers from this list - no sense planning on a player being available if they won't be
2. Add pitchers to the above plot so that I can...
3. ...put together a basic plan of attack for the draft
4. Generate a cheat sheet document to use for the draft

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE)
knitr::opts_knit$set(stop_on_error = 2L)
source("R/yahoo_api.R")
source("R/z_scores.R")
options(tidyverse.quiet=TRUE)
library(knitr)
library(plotly)
library(tidyverse)
```

@@

Some observations from this plot:

- Batters are in general weighed higher than pitchers since there are more categories with which to add to the z_sum
- Andrew Miller-like relievers are valued higher than ADP due to their high inning total and low ratio stats (ERA, WHIP)
- Ace starting pitchers and traditional closers are valued less than ADP despite their relative scarcity. 
  - Aces are the players most affected by not adjusting the z_score weighting for pitchers
  - Even with adjustment, tradtional closers have a lesser inning count nor have significant input in other categories to adjust their z_score very much

@@

@@

# Draft Prep
Armed with this information, here's what I need before the draft:

1. Exclude known keepers from this list - no sense planning on a player being available if they won't be
2. Add pitchers to the above plot so that I can...
3. ...put together a basic plan of attack for the draft
4. Generate a cheat sheet document to use for the draft
